Group Signatures Meet Anonymous Credentials: Or, How to Build Privacy Preserving Identities with Accountability

### 2022-02-22 prism-backend/research/gsac/uas-model.tex
Still working on non-frameability property of UAS.
Potentially correct non-frameability definition. Fixed issue in traceability too.

\commentwho{Jesus}{Maybe we could remove the attribute sets \uattrs, \dattrs,
  \tuattrs, \tdattrs, from the syntax, and assume that they are part of the
  signatures and/or credentials. This would certainly lead to a cleaner syntax,
  but, what impact would that have in other definitions, etc? Specifically, can
  we support selective disclosure credentials without them? (if so, \fissue,
  \feval and \finsp would be essential in doing so.); Right now, I am more in
  favour of tryint to remove the attribute sets from the definitions, as much
  as possible (and see if we can still support plain selective disclosure).}

@@

\todo{Domains (attributes, messages, etc.) are not correctly defined here. But
  for now, just leave it as is to at least convey the idea. Also, this needs
  refinement in general: what properties (if any) do these functions need to
  meet in order to be meaningful?}
\begin{description}
\item[$\fissue: (\uattrs,\dattrs) \rightarrow 0/1$.] Governs what customized
  conditions an issuer requires in order to issue credentials, when receiving
  a request from a user with a set of disclosed attributes \dattrs, and
  undisclosed attributes \uattrs (which need to be kept private from the
  issuer). \fissue returns 1 to accept a request, 0 to reject it.  
\item[$\feval: (\msg,\scred) \rightarrow 0/1$.] Governs customized conditions
  to define whether the owner of a set of credentials -- or, more specifically,
  credentials encoding certain attributes -- should be able to sign certain
  messages.
\item[$\finsp: (\upk,\scred,\sig) \rightarrow \bin^*$.] Defines what utility
  value, derived from the user's public key, credentials, and produced signature
  (or a subset thereof), should be extractable by the group inspector.
\end{description}

@@

\begin{description}
\item[\HIGEN.] Adds a new honest issuer to the game, by honestly generating
  its key pair.
\item[\CIGEN.] Adds a new corrupt issuer to the game or, if the specified issuer
  already exists and is honest, corrupts it.
\item[\HOGEN.] Adds a new honest inspector to the game, by honestly generating
  its key pair.
\item[\COGEN.] Adds a new corrupt inspector to the game or, if the specified
  inspector already exists and is honest, corrupts it. 
\item[\HUGEN.] Adds a new honest user to the game, by honestly generating
  the user's key pair.
\item[\CUGEN.] Adds a new corrupt user to the game or, if the specified
  user already exists and is honest, corrupts it.
\item[\OBTISS.] Lets the adversary add a new honestly generated credential to
  the game, on behalf of an honest user.
\item[\OBTAIN.] Enables the adversary to play the role of a dishonest issuer
  in games that support it, by letting it interact with honest users who want to
  receive credentials.
\item[\ISSUE.] Allows the adversary to play the role of dishonest users,
  requesting an honest issuer to produce credentials for them.
\item[\SIGN.] Lets the adversary get signatures from credentials belonging
  to honest users.
\item[\OPEN.] Given an honestly produced signature, lets the adversary learn
  which credential was used to produce it.
\item[\CHALb.] Upon receiving two challenge credentials, a common intersecting
  set of attributes, and a message, returns a signature produced by one of these
  two credentials, defined by the bit $b$, which is established in the anonymity
  game.
\end{description}

@@

        \procedure{$\HIGEN(\gid,\fissue)$}{%
          \pcif \gid \in \HI \lor \gid \in \CI: \pcreturn \bot \\
          (\ipk,\isk) \gets \IKeyGen(\parm) \\
          \IK[\gid] \gets (\ipk,\isk,\fissue) \\
          \HI \gets \HI \cup \lbrace \gid \rbrace \\
          \GK[\gid] \gets (\ipk,\fissue,\cdot,\cdot,\cdot) \\
          \pcreturn \ipk \\
        }

        \procedure{$\CIGEN(\gid,\ipk,\fissue)$}{%
          \pcif \gid \in \CI: \pcreturn \bot \\
          \CI \gets \CI \cup \lbrace \gid \rbrace \\          
          \pcif \gid \in \HI: \\
          \pcind \HI \gets \HI \setminus \lbrace \gid \rbrace; \\
          \pcind \pcreturn \IK[\gid] \\
          \pcelse: \IK[\gid] = (\ipk,\bot,\fissue) \\ 
          \GK[\gid] \gets (\ipk,\fissue,\cdot,\cdot,\cdot) \\         
          \pcreturn \top \\
        }

@@

        \procedure{$\HOGEN(\gid,\feval,\finsp)$}{%
          \pcif \gid \in \HO \lor \gid \in \CO: \pcreturn \bot \\
          (\opk,\osk) \gets \OKeyGen(\parm) \\
          \OK[\gid] \gets (\opk,\osk,\feval,\finsp) \\
          \HO \gets \HO \cup \lbrace  \gid \rbrace \\
          \GK[\gid] \gets (\cdot,\cdot,\opk,\feval,\finsp) \\          
          \pcreturn \opk \\
        }

        \procedure{$\COGEN(\gid,\opk,\feval,\finsp)$}{%
          \pcif \gid \in \CO: \pcreturn \bot \\
          \CO \gets \CO \cup \lbrace \gid \rbrace \\          
          \pcif \gid \in \HO: \\
          \pcind \HO \gets \HO \setminus \lbrace \gid \rbrace; \\
          \pcind \pcreturn \OK[\gid]) \\
          \pcelse: \OK[\gid] = (\opk,\bot,\feval,\finsp) \\
          \GK[\gid] \gets (\cdot,\cdot,\opk,\feval,\finsp) \\
          \pcreturn \top \\
        }

@@

        \procedure{$\ISSUE(\cid,\uid,\gid,\dattrs,
          \ldblbrace (\sgid,\scid,\tdattrs) \rdblbrace)$}{%
          \pcif \uid \notin \CU: \pcreturn \bot \\
          \pcif \gid \notin \HI: \pcreturn \bot \\
%          \pcif \exists \cid
          \pcif \exists \gid' \in \sgid~\st~\gid' \notin \HI: \pcreturn \bot \\
          \pcif \exists \cid' \in \scid~\st~\CRED[\cid'] \neq \bot: \pcreturn \bot \\
          \langle \cdot, \utrans \rangle \gets
          \langle \adv, \\
          \pcind \pcind
          \Issue(\PRVIK[\gid],\PUBUK[\uid],
          \ldblbrace (\GK[\sgid],\tdattrs)\rdblbrace) \rangle \\
          \trans[\cid] \gets \utrans \\
          \OWNR[\cid] \gets \uid;~\ATTR[\cid] \gets (\scid, \bot, \dattrs) \\
          \pcreturn \top \\          
        }

@@

        \procedure{$\CHALb(\msg,
          (\uid_{0,1},\uattrs_{0,1},\dattrs_{0,1},\ldblbrace (\sgid,\cscid_{0,1},\tuattrs_{0,1},\tdattrs_{0,1}) \rdblbrace))$}{%
          \pcif \cuid_0 \notin \HU \lor \cuid_1 \notin \HU: \pcreturn \bot \\
          \pcif \feval(\msg,\CRED[\scid_0]) \neq \feval(\msg,\CRED[\scid_1]):
          \pcreturn \bot \\
          \csig \gets \Sign(\PRVUK[\uid_b],\msg,\uattrs_b,\dattrs_b, \\
          \hspace*{42pt}
          \ldblbrace (\GK[\sgid],\CRED[\scid_b],\tuattrs_b,\tdattrs_b) \rdblbrace) \\
          \CSIG \gets \CSIG \cup
          \lbrace (\csig,\msg,\cscid_b,\uattrs_b,\dattrs_b,\sgid) \rbrace \\
          \pcreturn \csig
        }

@@

\begin{figure}[htp!]
  \procedure{$\ExpCorrect(1^\secpar)$}{%
    \parm \gets \Setup(1^\secpar) \\
    (\uid,\msg,\uattrs,\dattrs,
    \ldblbrace (\sgid,\scid,\tuattrs,\tdattrs) \rdblbrace)
    \gets \adv^{\HIGEN,\HOGEN,\HUGEN,\OBTISS}(\parm) \\
    \pcif \dattrs \nsubseteq \bigcup_{\cid \in \scid} \DATTR[\cid] \lor
    \bigcup \tdattrs \nsubseteq \dattrs: \pcreturn \bot \\
    \sig \gets \Sign(\PRVUK[\uid],\msg,\uattrs,\dattrs,
    \ldblbrace (\GK[\sgid],\CRED[\scid],\tuattrs,\tdattrs) \rdblbrace ) \\
    \pccomment{Signature fails to verify} \\
    \pcif \Verify(\sig,\msg,\dattrs,\GK[\sgid]) = 0: \pcreturn 0 \\
    \pccomment{An inspector among those involved in credentials used to produce
      \sig cannot inspect it} \\
    \pcif \exists \gid \in \sgid~\st~
    \Inspect(\PRVOK[\gid],\trans,\sig,\msg,\dattrs,
    \ldblbrace \GK[\sgid] \rdblbrace) = \bot: \pcreturn 0 \\
    \pccomment{Some of the produced $(\y,\iproof)$ pairs is rejected by
      \Judge \todo{This must be conditioned on \feval = 0!}} \\
    \pcif \exists \gid \in \sgid~\st~
    (\y,\iproof) \gets \Inspect(\PRVOK[\gid],\trans,\sig,\msg,\dattrs,
    \ldblbrace \GK[\sgid] \rdblbrace) \land \\
    \pcind
    \Judge(\y,\iproof,\sig,\msg,\dattrs,\ldblbrace \GK[\sgid] \rdblbrace) = 0):
    \pcreturn 0 \\
    \textrm{Let}~(\fissue^\gid,\feval^\gid,\finsp^\gid)~\textrm{denote the
      issue, evaluation and inspection functions defined} \\
    \textrm{by each $\gid \in \sgid$} \pccomment{\todo{Come up with some
        notation for this}} \\
    \pccomment{\fissue rejects some issued credential} \\
    \pcif \exists \gid \in \sgid~\st~\fissue^\gid(\tuattrs,\tdattrs) = 0:
    \pcreturn 0 \\
    \pccomment{\feval rejects the signature-message pair} \\
    \pcif \exists \gid \in \sgid~\st~\feval^\gid(\msg,\sig) = 0: \pcreturn 0 \\
    \pccomment{\y is the wrong value according to \finsp} \\
    \pcif \exists \gid \in \sgid~\st~
    \y \neq \finsp^\gid(\PUBUK[\uid],\CRED[\scid])): \pcreturn 0 \\
    \pcreturn 1
  }
  \caption{Correctness experiment for \UAS schemes. \todo{Reorganize this.}}
  \label{fig:exp-uas-corr}
\end{figure}

@@

In our notion of anonymity for \UAS, we need to merge the previous constraints.
Furthermore, a key difference with group signatures is that the game requires
the adversary to output credential identifiers, rather than user identifiers.
Specifically, this means that the adversary may actually output two credentials
that belong to the same user. Therefore, in some sense, the anonymity we get is
more general than that of group signatures. Moreover, in order to prevent
trivial wins by the adversary, we have to restrict that the challenge signatures
belong to a group that has been ``programmed'' with the same evaluation and
inspection functions, which is again a generalization over group signatures,
as discussed in the sequel. The formal specification of the anonymity game is
given in \figref{fig:exp-uas-anonb}.

\begin{figure}[htp!]
  \procedure{$\ExpAnonb(1^\secpar)$}{%
     \parm \gets \Setup(1^\secpar) \\
     (\cscid_0,\cscid_1,\status) \gets
     \adv^{\lbrace\HI,\CI,\HO,\CO,\HU,\CU\rbrace\GEN,\OBTAIN,\SIGN,\INSPECT}
     (\choose,\parm) \\
     b^* \gets
     \adv^{\lbrace\HI,\CI,\HO,\CO,\HU,\CU\rbrace,\GEN,\OBTAIN,\SIGN,\INSPECT,\CHALb}
     (\guess,\status) \\
     \pcreturn b^*
  }
  \caption{Anonymity experiment for \UAS schemes.}
  \label{fig:exp-uas-anonb}
\end{figure}

@@

Our notion of traceability for \UAS is inspired by both. First, we restrict to
signatures that are accepted by \Verify. For any such signature, \Inspect has to
create a valid output (i.e., must not abort). The output of \Inspect has to be
accepted by \Judge too. Moreover, there must exist one user (either honest or
corrupt) who used his public key to obtain one or more credentials that allowed
him to produce a signature which, once inspected, returns \y.

\begin{figure}[htp!]
  \procedure{$\ExpTrace(1^\secpar)$}{%
    \parm \gets \Setup(1^\secpar) \\
    \pccomment{\todo{Right now, in \COGEN we may not know \osk! Then, the checks
        in the last part of the game may not be executable!}} \\
     (\sig,\dattrs,\msg) \gets
     \adv^{\lbrace \HI,\CO,\HU,\CU \rbrace \GEN,\OBTISS,\ISSUE,\SIGN,\INSPECT}
     (\parm) \\
     \pcreturn 1~\pcif \Verify(\sig,\msg,\dattrs,\GK[\sgid]) = 1~\land~( \\
     \pcind \pccomment{All \Obtain transcripts fail to open \sig} \\
     \pcind \nexists \gid \in \sgid:
     \Inspect(\PRVOK[\gid],\trans,\sig,\msg,\dattrs,\sgid) = \bot~\lor \\
     \pcind \pccomment{Such transcript exists, but ...} \\
     \pcind \exists\gid \in \sgid~\st~
     \Inspect(\PRVOK[\gid],\trans,\sig,\msg,\dattrs) =
     (\y,\iproof)~\land (\\
     \pcind \pcind \pccomment{... the proof is rejected by \Judge ...} \\
     \pcind \pcind \Judge(\y,\iproof,\sig,\msg,\dattrs,\GK[\sgid]) = 0~\lor \\
     \pcind \pcind \pccomment{... or \Judge accepts the proof, but inspect
       returns an invalid value} \\
     \pcind \pcind \nexists \uid \in \CU \cup \HU~\st~
     \y = \finsp(\PUBUK[\uid],\CRED[\uid],\sig) \\
     \pcind ) \\
     ) \\
     \pcreturn 0
  }
  \caption{Traceability experiment for \UAS schemes.}
  \label{fig:exp-uas-trace}
\end{figure}

@@

\paragraph{Non-frameability.} %
Non-frameability variants are a core unforgeability-type property in group
signatures. However, no
similar property is modeled for anonymous credentials (\todo{see the discussion
  in \secref{sec:introduction} for further detail}). It is a quite strong
property, as it must be ensured even in the presence of dishonest issuer and
opener. Intuitively, it prevents the adversary from creating a signature that
frames an honest user. Depending on the inspection capabilities of the scheme,
this framing could be done in different ways; i.e., by convincing third parties
that signatures by different (possibly corrupt) users are linked, or directly
by having open proofs output the identity of a user who did not create the
signature being opened.
%
In \UAS schemes, in order for a user to be framed...

\begin{figure}[htp!]
  \procedure{$\ExpNonframe(1^\secpar)$}{%
    \parm \gets \Setup(1^\secpar) \\
     (\sig,\dattrs,\msg,\upk,\cred,\oproof) \gets
     \adv^{\lbrace\CI,\CO,\HU,\CU\rbrace\GEN,\OBTAIN,\SIGN}(\parm) \\
     \pcreturn 1~\pcif \Verify(\gpk,\sig,\dattrs,\msg) = 1 \land
     \OWNR[\cred] \in \HU \\%\land \cred \notin \CCRED~\land\\
     \pcind \Judge(\gpk,\upk,\cred,\oproof,\sig,\dattrs,\msg) = 1~\land \\
     \pcind \pccomment{\sig was not produced by \SIGN, or \upk and \cred do not match} \\
     \pcind (\sig \notin \SIG[\OWNR[\cred]] \lor \PUBUK[\OWNR[\cred]] \neq \upk) \\
     \pcreturn 0
  }
  \caption{Non-frameability experiment for \GSAC schemes.}
  \label{fig:exp-gsac-frame}
\end{figure}

>>>>

\commentwho{Jesus}{Maybe we could remove the attribute sets \uattrs, \dattrs,
  \tuattrs, \tdattrs, from the syntax, and assume that they are part of the
  signatures and/or credentials. This would certainly lead to a cleaner syntax,
  but, what impact would that have in other definitions, etc? Specifically, can
  we support selective disclosure credentials without them? (if so, \fissue,
  \feval and \finsp would be essential in doing so.); Right now, I am more in
  favour of trying to remove the attribute sets from the definitions, as much
  as possible (and see if we can still support plain selective disclosure).}

@@

\todo{Domains (attributes, messages, etc.) are not correctly defined here. But
  for now, just leave it as is to at least convey the idea. Also, this needs
  refinement in general: what properties (if any) do these functions need to
  meet in order to be meaningful?}
\begin{description}
\item[$\fissue: (\uattrs,\dattrs) \rightarrow 0/1$.] Governs what customized
  conditions an issuer requires in order to issue credentials, when receiving
  a request from a user with a set of disclosed attributes \dattrs, and
  undisclosed attributes \uattrs (which need to be kept private from the
  issuer). \fissue returns 1 to accept a request, 0 to reject it.  
\item[$\feval: (\upk,\scred,\msg) \rightarrow 0/1$.] Governs customized
  conditions to define whether the owner of a user key and set of credentials --
  or, more specifically, credentials encoding certain attributes -- should be
  able to sign certain messages.
\item[$\finsp: (\upk,\scred,\msg,\sig) \rightarrow \bin^*$.] Defines what
  utility value, derived from the user's public key, credentials, signed
  message, and produced signature (or a subset thereof), should be extractable
  by the group inspector.
\end{description}

@@

\begin{description}
\item[\IGEN.] Adds a new issuer to the game, generating its keypair and setting
  the associated issuance function.
\item[\OGEN.] Adds a new inspector to the game, generating its key pair and
  setting the associated evaluation and inspection functions.
\item[\HUGEN.] Adds a new honest user to the game, by honestly generating
  the user's key pair.
\item[\CUGEN.] Adds a new corrupt user to the game or, if the specified
  user already exists and is honest, corrupts it.
\item[\OBTISS.] Lets the adversary add a new honestly generated credential to
  the game, on behalf of an honest user.
\item[\OBTAIN.] Enables the adversary to play the role of a dishonest issuer
  in games that support it, by letting it interact with honest users who want to
  receive credentials.
\item[\ISSUE.] Allows the adversary to play the role of dishonest users,
  requesting an honest issuer to produce credentials for them.
\item[\SIGN.] Lets the adversary get signatures from credentials belonging
  to honest users.
\item[\OPEN.] Given an honestly produced signature, lets the adversary learn
  which credential was used to produce it.
\item[\CHALb.] Upon receiving two challenge credentials, a common intersecting
  set of attributes, and a message, returns a signature produced by one of these
  two credentials, defined by the bit $b$, which is established in the anonymity
  game.
\end{description}

@@

        \procedure{$\IGEN(\gid,\fissue)$}{%
          \pcif \gid \in \HI \lor \gid \in \CI: \pcreturn \bot \\
          (\ipk,\isk) \gets \IKeyGen(\parm) \\
          \IK[\gid] \gets (\ipk,\isk,\fissue) \\
          \HI \gets \HI \cup \lbrace \gid \rbrace \\
          \GK[\gid] \gets (\ipk,\fissue,\cdot,\cdot,\cdot) \\
          \pcreturn \ipk \\
        }

        \procedure{$\ICORR(\gid)$}{%
          \pcif \gid \in \CI \lor \gid \notin \HI: \pcreturn \bot \\
          \HI \gets \HI \setminus \lbrace \gid \rbrace \\
          \CI \gets \CI \cup \lbrace \gid \rbrace \\
          \pcreturn \isk \\
        }

@@

        \procedure{$\OGEN(\gid,\feval,\finsp)$}{%
          \pcif \gid \in \HO \lor \gid \in \CO: \pcreturn \bot \\
          (\opk,\osk) \gets \OKeyGen(\parm) \\
          \OK[\gid] \gets (\opk,\osk,\feval,\finsp) \\
          \HO \gets \HO \cup \lbrace \gid \rbrace \\
          \GK[\gid] \gets (\cdot,\cdot,\opk,\feval,\finsp) \\
          \pcreturn \opk \\
        }

        \procedure{$\OCORR(\gid)$}{%
          \pcif \gid \in \CO \lor \gid \notin \HO: \pcreturn \bot \\
          \HO \gets \HO \setminus \lbrace \gid \rbrace \\
          \CO \gets \CO \cup \lbrace \gid \rbrace \\
          \pcreturn \osk \\
        }

@@

        \procedure{$\ISSUE(\cid,\uid,\gid,\dattrs,
          \ldblbrace (\sgid,\scid,\tdattrs) \rdblbrace)$}{%
          \pcif \uid \notin \CU: \pcreturn \bot \\
          \pcif \gid \notin \HI: \pcreturn \bot \\
          \pcif \exists \gid' \in \sgid~\st~\gid' \notin \HI: \pcreturn \bot \\
          \pcif \exists \cid' \in \scid~\st~\CRED[\cid'] \neq \bot: \pcreturn \bot \\
          \langle \cdot, \utrans \rangle \gets
          \langle \adv, \\
          \pcind \pcind
          \Issue(\PRVIK[\gid],\PUBUK[\uid],
          \ldblbrace (\GK[\sgid],\tdattrs)\rdblbrace) \rangle \\
          \trans[\cid] \gets \utrans \\
          \OWNR[\cid] \gets \uid;~\ATTR[\cid] \gets (\scid, \bot, \dattrs) \\
          \pcreturn \top \\          
        }

@@

        \procedure{$\CHALb(\msg,
          (\uid_{0,1},\uattrs_{0,1},\dattrs_{0,1},\ldblbrace (\sgid,\cscid_{0,1},
          \tuattrs_{0,1},\tdattrs_{0,1}) \rdblbrace))$}{%          
          \pcif \cuid_0 \notin \HU \lor \cuid_1 \notin \HU: \pcreturn \bot \\
          \pcif \exists \gid \in \sgid~\st~\gid \in \CO: \pcreturn \bot \\
          \pcif \feval(\msg,\CRED[\scid_0]) \neq \feval(\msg,\CRED[\scid_1]):
          \pcreturn \bot \\
          \csig \gets \Sign(\PRVUK[\uid_b],\msg,\uattrs_b,\dattrs_b, \\
          \hspace*{42pt}
          \ldblbrace (\GK[\sgid],\CRED[\scid_b],\tuattrs_b,\tdattrs_b) \rdblbrace) \\
          \CSIG \gets \CSIG \cup
          \lbrace (\csig,\msg,\cscid_b,\uattrs_b,\dattrs_b,\sgid) \rbrace \\
          \pcreturn \csig
        }

@@

\begin{figure}[htp!]
  \procedure{$\ExpCorrect(1^\secpar)$}{%
    \parm \gets \Setup(1^\secpar) \\
    (\uid,\msg,\uattrs,\dattrs,
    \ldblbrace (\sgid,\scid,\tuattrs,\tdattrs) \rdblbrace)
    \gets \adv^{\IGEN,\OGEN,\HUGEN,\OBTISS}(\parm) \\
    \pcif \dattrs \nsubseteq \bigcup_{\cid \in \scid} \DATTR[\cid] \lor
    \bigcup \tdattrs \nsubseteq \dattrs: \pcreturn \bot \\
    \sig \gets \Sign(\PRVUK[\uid],\msg,\uattrs,\dattrs,
    \ldblbrace (\GK[\sgid],\CRED[\scid],\tuattrs,\tdattrs) \rdblbrace ) \\
    \pccomment{Signature fails to verify} \\
    \pcif \Verify(\sig,\msg,\dattrs,\GK[\sgid]) = 0: \pcreturn 0 \\
    \pccomment{An inspector among those involved in credentials used to produce
      \sig cannot inspect it} \\
    \pcif \exists \gid \in \sgid~\st~
    \Inspect(\PRVOK[\gid],\trans,\sig,\msg,\dattrs,
    \ldblbrace \GK[\sgid] \rdblbrace) = \bot: \pcreturn 0 \\
    \pccomment{Some of the produced $(\y,\iproof)$ pairs is rejected by
      \Judge \todo{This must be conditioned on \feval = 0!}} \\
    \pcif \exists \gid \in \sgid~\st~
    (\y,\iproof) \gets \Inspect(\PRVOK[\gid],\trans,\sig,\msg,\dattrs,
    \ldblbrace \GK[\sgid] \rdblbrace) \land \\
    \pcind
    \Judge(\y,\iproof,\sig,\msg,\dattrs,\ldblbrace \GK[\sgid] \rdblbrace) = 0):
    \pcreturn 0 \\
    \textrm{Let}~(\fissue^\gid,\feval^\gid,\finsp^\gid)~\textrm{denote the
      issue, evaluation and inspection functions defined} \\
    \textrm{by each $\gid \in \sgid$} \pccomment{\todo{Come up with some
        notation for this}} \\
    \pccomment{\fissue rejects some issued credential} \\
    \pcif \exists \gid \in \sgid~\st~\fissue^\gid(\tuattrs,\tdattrs) = 0:
    \pcreturn 0 \\
    \pccomment{\feval rejects the signature-message pair} \\
    \pcif \exists \gid \in \sgid~\st~\feval^\gid(\msg,\sig) = 0: \pcreturn 0 \\
    \pccomment{\y is the wrong value according to \finsp} \\
    \pcif \exists \gid \in \sgid~\st~
    \y \neq \finsp^\gid(\PUBUK[\uid],\CRED[\scid])): \pcreturn 0 \\
    \pcreturn 1
  }
  \caption{Correctness experiment for \UAS schemes. \todo{Reorganize this.}}
  \label{fig:exp-uas-corr}
\end{figure}

@@

In our notion of anonymity for \UAS, we need to merge the previous constraints.
Furthermore, a key difference with group signatures is that the game requires
the adversary to output credential identifiers, rather than user identifiers.
Specifically, this means that the adversary may actually output two credentials
that belong to the same user. Therefore, in some sense, the anonymity we get is
more general than that of group signatures. Moreover, in order to prevent
trivial wins by the adversary, we have to restrict that the challenge signatures
belong to a group that has been ``programmed'' with the same evaluation and
inspection functions, which is again a generalization over group signatures,
as discussed in the sequel. The formal specification of the anonymity game is
given in \figref{fig:exp-uas-anonb}, where $\Oanonc \gets (\lbrace\HU,\CU\rbrace
\GEN,\lbrace\II,\OO\rbrace\GEN,\lbrace\II,\OO\rbrace\CORR,\OBTAIN,\SIGN,
\INSPECT)$ and $\Oanong \gets (\lbrace\HU,\CU\rbrace\GEN,\lbrace\II,\OO\rbrace
\GEN,\lbrace\II,\OO\rbrace,\CORR,\OBTAIN,\SIGN,\INSPECT,\CHALb)$

\begin{figure}[htp!]
  \procedure{$\ExpAnonb(1^\secpar)$}{%
     \parm \gets \Setup(1^\secpar) \\
     (\cscid_0,\cscid_1,\status) \gets \adv^{\Oanonc}(\choose,\parm) \\
     b^* \gets \adv^{\Oanong} (\guess,\status) \\
     \pcreturn b^*
  }
  \caption{Anonymity experiment for \UAS schemes.}
  \label{fig:exp-uas-anonb}
\end{figure}

@@

Our notion of traceability for \UAS is inspired by both. First, we restrict to
signatures that are accepted by \Verify. For any such signature, \Inspect has to
create a valid output (i.e., must not abort). The output of \Inspect has to be
accepted by \Judge too. Moreover, there must exist one user (either honest or
corrupt) who used his public key to obtain one or more credentials that allowed
him to produce a signature which, once inspected, returns \y. The formal
definition of the traceability experiment is given in \figref{fig:exp-uas-trace},
where $\Otrace \gets \lbrace\HU,\CU\rbrace\GEN,\IGEN,\OGEN,\OCORR,\OBTISS,
\ISSUE,\SIGN,\INSPECT$.

\begin{figure}[htp!]
  \procedure{$\ExpTrace(1^\secpar)$}{%
    \parm \gets \Setup(1^\secpar) \\
     (\sig,\dattrs,\msg) \gets
     \adv^{\Otrace}(\parm) \\
     \pcreturn 1~\pcif \Verify(\sig,\msg,\dattrs,\GK[\sgid]) = 1~\land~( \\
     \pcind \pccomment{All \Obtain transcripts fail to open \sig} \\
     \pcind \nexists \gid \in \sgid:
     \Inspect(\PRVOK[\gid],\trans,\sig,\msg,\dattrs,\sgid) = \bot~\lor \\
     \pcind \pccomment{Such transcript exists, but ...} \\
     \pcind \exists\gid \in \sgid~\st~
     \Inspect(\PRVOK[\gid],\trans,\sig,\msg,\dattrs) =
     (\y,\iproof)~\land (\\
     \pcind \pcind \pccomment{... the proof is rejected by \Judge ...} \\
     \pcind \pcind \Judge(\y,\iproof,\sig,\msg,\dattrs,\GK[\sgid]) = 0~\lor \\
     \pcind \pcind \pccomment{... or \Judge accepts the proof, but inspect
       returns an invalid value} \\
     \pcind \pcind \nexists \uid \in \CU \cup \HU~\st~
     \y = \finsp(\PUBUK[\uid],\CRED[\uid],\sig) \\
     \pcind ) \\
     ) \\
     \pcreturn 0
  }
  \caption{Traceability experiment for \UAS schemes.}
  \label{fig:exp-uas-trace}
\end{figure}

@@

Finally, note that we can only ensure consistency of the value returned by
\finsp, for all users, as long as the issuer is honest. This follows from the
fact that \finsp depends on the user key pair and the credentials that are
issued to each user. Therefore, a dishonest issuer could create untraceable
credentials (i.e., issue credentials without updating the \trans table), so that
the \finsp function outputs whatever desired value, yet it cannot be traced to
any registered user. That is, this minimality argument is just a generalization
of the one described in \cite[Section 4.3]{bsz05}. This is also consistent with
the unforgeability requirement of anonymous credentials systems, as a corrupt
issuer can grant arbitrary credentials to any user, and therefore honest
issuers are required.

\paragraph{Non-frameability.} %
Non-frameability variants are a core unforgeability-type property in group
signatures. However, no
similar property is modeled for anonymous credentials (\todo{see the discussion
  in \secref{sec:introduction} for further detail}). It is a quite strong
property, as it must be ensured even in the presence of dishonest issuer and
opener. Intuitively, it prevents the adversary from creating a signature that
frames an honest user. Depending on the inspection capabilities of the scheme,
this framing could be done in different ways; i.e., by convincing third parties
that signatures by different (possibly corrupt) users are linked, or directly
by having open proofs output the identity of a user who did not create the
signature being opened.
%
In \UAS schemes, in order for a user to be framed \todo{...}. The
non-frameability property for \UAS schemes is formally defined in
\figref{fig:exp-uas-frame}, where $\Oframe \gets \lbrace\HU,\CU\rbrace\GEN,
\lbrace\II,\OO\rbrace\GEN,\lbrace\II,\OO\rbrace\CORR,\OBTAIN,\SIGN$

\begin{figure}[htp!]
  \procedure{$\ExpNonframe(1^\secpar)$}{%
    \parm \gets \Setup(1^\secpar) \\
     (\sig,\dattrs,\msg,\sgid,\y,\iproof) \gets
     \adv^{\Oframe}(\parm) \\
     \pcreturn 1~\pcif \Verify(\sig,\msg,\dattrs,\GK[\sgid]) = 1 \land
     \Judge(\y,\iproof,\sig,\msg,\dattrs,\GK[\sgid]) = 1~\land \\
     \pcind \exists \uid \in \HU~\st~\Identify(\PRVUK[\uid],\sig) = 1 \land
     \sig \notin \SIG[\uid] \\
     \pcreturn 0
  }
  \caption{Non-frameability experiment for \UAS schemes.}
  \label{fig:exp-uas-frame}
\end{figure}
